---
title: "Analysis2.0"
author: "Arkajyoti Bhattacharjee"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read and create databases for analysis

```{r echo = TRUE,eval = FALSE}
database <- read.table("database.csv", header = TRUE, sep = ",")
#View(database)
library(tidyverse)
database <- database %>%
  mutate(RGDP2019 = (GDP2019-GDP2018)/GDP2018)
db19 <- database %>%
  select(matches('country|2019')) # add RGDP, rate of change in GDP from 2018-2019
db19 <- select(db19, -GDP2019) # drop GDP2019 
#View(db19)
dim(db19)
# formatting NFCR column
db19[, "NFCR2019"] <- sapply(db19[,"NFCR2019"], function (x) gsub('%', '', x))
db19[,"NFCR2019"] <- as.numeric(db19[,"NFCR2019"])
#str(db19)

#check the number of NAs per column
apply(is.na(db19), 2, sum)

#db19woNA <- na.omit(db19) # db19 without NA
```


# Exploratory Data Analysis

```{r echo = TRUE, eval = TRUE, warning=FALSE}
library(GGally)
ggpairs(db19[, -1], progress = FALSE, 
        columnLabels = c("NFCR", "CPI", "AML", "ARR", "WES", "GE", "PV", "RQ", 
                         "RL", "VA", "RGDP")) 

# From the scatterplot matrix, we see that RL and CPI have a high correlation (0.902), along with GE & RL (0.943), GE & RQ (0.9370), and RQ & RL (0.929).
## indicative of multicollinearity
# The distribution of NFCR seems to be heavy-tailed.
# log transforms??
# all are continuous variables
# predictors don't seem to be related to the response much
# We drop RL, RQ(why?--common to CPI, RQ, & GE, Y IS RELATED MORE TO CPI AND GE,
# RQ AND GE ARE SIMILAR INTUTITIVELY)
# EXPLAIN HOW TH RELATIONSHIP IS INTUITIVE?!
ggpairs(db19[, -c(1, 7, 10)], progress = FALSE, 
        columnLabels = c("NFCR", "CPI", "AML", "ARR", "WES", "PV", "RQ", 
                         "VA", "RGDP"))

# OTHER SUMMARY PLOTS
subdb19 <- select(db19, c(GE2019, PV2019, VA2019))
#install.packages("reshape2")
library(reshape2)
melted.data <- melt(subdb19)
View(melted.data)
p1 <- ggplot(data = melted.data, aes(x=variable, y=value))+
  geom_boxplot(aes(fill = variable)) + #violin plot 
  labs(
    x= "Governance Quality"
  )
p1

p2 <- ggplot(data = db19, aes(x=NFCR2019))+
  geom_histogram(aes(y=..density..), fill = "magenta")+
  geom_density(color="red")
p3 <- ggplot(data = db19, aes(x=CPI2019))+
  geom_histogram(aes(y=..density..), fill = "seagreen")+
  geom_density(color="red")
p4 <- ggplot(data = db19, aes(x=AML2019))+
  geom_histogram(aes(y=..density..), fill = "orange")+
  geom_density(color="red")
p5 <- ggplot(data = db19, aes(x=WES2019))+
  geom_histogram(aes(y=..density..), fill = "cyan")+
  geom_density(color="red")

# install.packages("patchwork")
library(patchwork)
(p2 +p3)/(p4 + p5)

# world map + heat map of values of all variables
install.packages("maps")
library(maps)
library(data.table)
world_map <- map_data("world")

##rename Country to region in db19
db19.renamed <- db19
names(db19.renamed)[1]<- "region" 

joined.data  <- left_join(world_map, db19.renamed, by = "region")
joined.data <- na.omit(joined.data)

map1 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=ARR2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map1 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=NFCR2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map2 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=CPI2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map3 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=AML2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map4 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=ARR2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map5 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=WES2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map6 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=GE2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map7 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=PV2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map8 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=VA2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 
map9 <- ggplot(joined.data, aes(x = long, y = lat, group = group))+
  geom_map(map = world_map, aes(x=long, y = lat, map_id= region), color =  "black", fill = "white")+
  geom_polygon(aes(fill=RGDP2019)) +
  scale_fill_viridis_c(option = "turbo", trans = "sqrt") 

(map1 + map2 + map3)/(map4 + map5 + map6)/(map7 + map8 + map9)
```

# Methods and Model Building

## Transformation of Predictors

```{r echo = TRUE, EVAL = TRUE}
#install.packages("car")
library(car)
summary(powerTransform(cbind(CPI2019,  AML2019,  ARR2019,  WES2019, GE2019,
                             PV2019,  VA2019, RGDP2019)~1, data = db19,
                       family = 'yjPower'))
```
Based on the above transformations, we do not prefer 1.34 for `PV2019` and 2 for `VA2019` for interpretability issues. But let's keep them to see how R^2 is affect. Call it `model.noninterpretable`

## Variable Selection

```{r echo = TRUE, eval = TRUE}
#install.packages("leaps")
library(leaps)
## yeo-johnson transformation 
install.packages("VGAM")
library(VGAM)

(summary_best_subset<-summary(regsubsets(NFCR2019~ 
    yeo.johnson(CPI2019, 0.5) + AML2019 + yeo.johnson(ARR2019, 0) + WES2019 + GE2019 + 
        PV2019 + VA2019 + RGDP2019, 
    data = na.omit(db19))))
which.max(summary_best_subset$adjr2)

## Based on this, we choose sqrt(CPI2019), log(ARR2019), WES(2019), PV2019, VA2019, RGDP2019,
## although optimal is log(ARR2019), WES(2019), PV2019, VA2019

## THis is for the non-interpretable model

(summary_best_subset2<-summary(regsubsets(NFCR2019~ 
    yeo.johnson(CPI2019, 0.5) + AML2019 + yeo.johnson(ARR2019,0) + WES2019 + GE2019 + 
        yeo.johnson(PV2019,1.34) + yeo.johnson(VA2019, 2)  + RGDP2019, 
    data = na.omit(db19))))
which.max(summary_best_subset$adjr2)
## Based on this we choose (optimal) logARR, WES, PV, VA

## Verify if transformations a re required again
summary(powerTransform(cbind(yeo.johnson(CPI2019, 0.5) + AML2019 + 
                                yeo.johnson(ARR2019, 0) + WES2019 + GE2019 +
                                PV2019 + VA2019 + RGDP2019)~1, data = na.omit(db19),
                       family = 'yjPower'))

## no change

summary(powerTransform(cbind(yeo.johnson(ARR2019,0) +
                               WES2019 + yeo.johnson(PV2019,1.34) +
                               yeo.johnson(VA2019, 2))~1, 
                             data = na.omit(db19),
                       family = 'yjPower'))

## No change required
```

## Transformation of the response


```{r echo = TRUE, eval = TRUE}


summary(powerTransform(lm(NFCR2019~ yeo.johnson(CPI2019, 0.5) + 
                            yeo.johnson(ARR2019, 0) + WES2019 + 
                            PV2019 + VA2019 + RGDP2019, 
                          data = na.omit(db19)),
                       family = 'yjPower'))
## suggests y^1.62

summary(powerTransform(lm(NFCR2019~yeo.johnson(ARR2019, 0) + WES2019 + 
                            PV2019 + VA2019,
                          data = na.omit(db19)),
                       family = 'yjPower'))
## suggests y^1.62

summary(powerTransform(lm(NFCR2019~ yeo.johnson(ARR2019, 0) + WES2019 + 
                            yeo.johnson(PV2019,1.34) +
                               yeo.johnson(VA2019, 2),
                          data = na.omit(db19)),
                       family = 'yjPower'))
## suggests y^1.62
```

## Model Building

```{r echo =TRUE, eval = TRUE}
## yeo-johnson transformation 
install.packages("VGAM")
library(VGAM)
NFCR19 <- yeo.johnson(na.omit(db19)[, "NFCR2019"], lambda = 1.62) 

mod1 <- lm(NFCR19~ yeo.johnson(ARR2019, 0) + WES2019 + 
                            yeo.johnson(PV2019,1.34) +
                               yeo.johnson(VA2019, 2),
                          data = na.omit(db19))
mod2 <- lm(NFCR2019~yeo.johnson(ARR2019, 0) + WES2019 + 
                            PV2019 + VA2019,
                          data = na.omit(db19))

mod3 <- lm(NFCR2019~ yeo.johnson(CPI2019, 0.5) + 
                            yeo.johnson(ARR2019, 0) + WES2019 + 
                            PV2019 + VA2019 + RGDP2019, 
                          data = na.omit(db19))
summary(mod1)
summary(mod2) # best adj R^2
summary(mod3) # second best

plot(mod2)
plot(mod3)


```

## ACE Algorithm

```{r echo = TRUE,eval = TRUE}
install.packages("acepack")
library(acepack)
db19noNA <- na.omit(db19)
ACE <- ace(y = db19noNA[, 2], x = as.matrix(db19noNA[, -c(1, 2)]))
model.ace <- lm(ACE$ty~ACE$tx)
summary(model.ace)

for(i in names(db19)[-c(1,2)]) plot(db19noNA[, i], ACE$tx[, i])
```














