---
title: "Analysis"
author: "Arkajyoti Bhattacharjee"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read and create databases for analysis

```{r echo = TRUE,eval = FALSE}
database <- read.table("database.csv", header = TRUE, sep = ",")
#View(database)
#library(tidyverse)
database <- database %>%
  mutate(RGDP2019 = (GDP2019-GDP2018)/GDP2018)
db19 <- database %>%
  select(matches('country|2019')) # add RGDP, rate of change in GDP from 2018-2019
db19 <- select(db19, -GDP2019) # drop GDP2019 
#View(db19)
dim(db19)
# formatting NFCR column
db19[, "NFCR2019"] <- sapply(db19[,"NFCR2019"], function (x) gsub('%', '', x))
db19[,"NFCR2019"] <- as.numeric(db19[,"NFCR2019"])
#str(db19)

#check the number of NAs per column
apply(is.na(db19), 2, sum)

db19woNA <- na.omit(db19) # db19 without NA
```

# Scatterplot Matrix

```{r echo = TRUE, eval = TRUE}
library(GGally)
ggpairs(db19woNA[, 2:12], progress = FALSE)
```

# Transformation of Predictors

```{r echo = TRUE, EVAL = TRUE}
#install.packages("car")
library(car)
summary(powerTransform(cbind(CPI2019,  AML2019,  ARR2019,  WES2019, GE2019,   PV2019,   RQ2019,   RL2019,   VA2019, RGDP2019)~1, data = db19woNA, family = 'yjPower'))
```
# Transformation of Response

```{r echp = TRUE, eval = TRUE}
set.seed(57)
summary(powerTransform(lm(  1/(NFCR2019+runif(nrow(db19woNA), max=0.5)) ~ CPI2019 + AML2019 + log(ARR2019) + WES2019 +
                            I(GE2019^1.2) + I(PV2019^.4) + RQ2019 + RL2019 + I(VA2019^2) +
                            RGDP2019, data= db19woNA ), family = 'yjPower'))
```
# Model


```{r ecgho = TRUE, eval = TRUE}
set.seed(57)
mod1 <- lm(1/(NFCR2019 + runif(nrow(db19woNA), max=0.5)) ~ CPI2019 + AML2019 + log(ARR2019) + WES2019 +
                            I(GE2019^1.2) + I(PV2019^1.4) + RQ2019 + RL2019 + I(VA2019^2) +
                            RGDP2019, data= db19woNA)
summary(mod1)
```

```{r echo = TRUE, eval = TRUE}
set.seed(57)
pairs(formula = 1/(NFCR2019 + runif(nrow(db19woNA), max = 0.5)) ~ 
    CPI2019 + AML2019 + log(ARR2019) + WES2019 + I(GE2019^1.2) + 
        I(PV2019^1.4) + RQ2019 + RL2019 + I(VA2019^2) + RGDP2019, 
    data = db19woNA)
```


# Variable Selection

```{r echo = TRUE, eval = TRUE}
#install.packages("leaps")
library(leaps)
summary_best_subset <- summary(regsubsets(NFCR2019~ 
    CPI2019 + AML2019 + log(ARR2019) + WES2019 + GE2019 + 
        PV2019 + RQ2019 + RL2019 + VA2019 + RGDP2019, 
    data = db19woNA))
which.max(summary_best_subset$adjr2)
```
```{r echo = TRUE, eval = TRUE}
summary_best_subset <- summary(regsubsets(NFCR2019~ 
    CPI2019 + AML2019 + ARR2019 + WES2019 + GE2019 + 
        PV2019 + RQ2019 + RL2019 + VA2019 + RGDP2019, 
    data = db19woNA))
which.max(summary_best_subset$adjr2)
```









```{r echo = TRUE, eval = TRUE}
#install.packages("olsrr")
library(olsrr)
k <- ols_step_both_p(lm(NFCR2019~ 
    CPI2019 + AML2019 + log(ARR2019) + WES2019 + GE2019 + 
        PV2019 + RQ2019 + RL2019 + VA2019 + RGDP2019, 
    data = db19woNA))
plot(k)
summary(k)
```

```{r}
mod0 <- lm(NFCR2019~.-Country-RL2019-RQ2019-GE2019, data = db19woNA)
summary(mod0)
#plot(mod0)
#library(car)
vif(mod0)
#library(GGally)
ggpairs(db19woNA[, c(2,3,4,5,6,8,11,12)], progress= FALSE)
```


See that `RL2019` and `CPI2019` are highly correlated (0.967); RQ and GE are also same(0.946)

So, choose CPI as - all non-negative, no NAs.

Note - base model - includes everything has adj R^2 0.166. worst possible case!
- RL : 0.1658
- RL, RQ: 0.1587
- RL, RQ, GE: 0.1519

# Transformation of Predictors

```{r echo = TRUE, EVAL = TRUE}
#install.packages("car")
library(car)
summary(powerTransform(cbind(CPI2019,  AML2019,  ARR2019,  WES2019, PV2019,
                             VA2019, GDP2019)~1, data = db19woNA, family = 'yjPower'))
```
# Variable Selection

```{r echo = TRUE, eval = TRUE}
#install.packages("leaps")
library(leaps)
(summary_best_subset <- summary(regsubsets(1/(1+exp(-db19woNA[,"NFCR2019"]))~ 
    sqrt(CPI2019) + AML2019 + log(ARR2019) + WES2019 + 
        PV2019 + VA2019 + log(GDP2019), 
    data = db19woNA)))
which.max(summary_best_subset$adjr2)

mod1 <- lm(1/(1+exp(-db19woNA[,"NFCR2019"]))~ 
    AML2019 + log(ARR2019) + WES2019 + 
       PV2019 + VA2019 + log(GDP2019), 
    data = db19woNA) 
summary(mod1)

summary(powerTransform(lm(1/(1+exp(-db19woNA[,"NFCR2019"])) ~ sqrt(CPI2019) + AML2019 + log(ARR2019) + WES2019 + 
        I(PV2019^1.37) + I(VA2019^2) + log(GDP2019), 
    data = db19woNA), family = 'yjPower'))


moddata <- data.frame(1/(1+exp(-db19woNA[,"NFCR2019"])),sqrt(db19woNA[, "CPI2019"]), db19woNA[, "AML2019"],
                 log(db19woNA[,"ARR2019"]), db19woNA[,"WES2019"], db19woNA[,"PV2019"],
                 db19woNA[,"VA2019"]^2, log(db19woNA[,"GDP2019"]))

ggpairs(moddata, progress = FALSE,  
                 columnLabels  = c("NFCR", "CPI", "AML", "ARR", "WES", "PV",
                             "VA", "GDP"))
```
# model fit after all sorts of transformations



```{r e cho = TRUE, eval =TRUE }
mod3 <- lm(NFCR2019 ~ log(ARR2019) + WES2019 + 
        PV2019 + VA2019 + log(GDP2019), 
    data = db19woNA)
summary(mod3)
```




